Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-23 docs/manuscript/manuscript.tex

\begin{table}[ht]
    \centering
    \begin{tabular}{c|c}
         &  \\
         & 
    \end{tabular}
    \caption{Performance metric summaries across the four scenarios}
    \label{tab:my_label}
\end{table}

@@

\bibliography{ai-trees-references}

>>>>

\begin{table}[ht]\small
    \centering
\begin{tabular}{@{}llllll@{}}
\toprule
\textbf{Scenario} & \textbf{Averaging method} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} & \textbf{Support} \\ \midrule
Pr\_Im    & Probable            & 0.9  & 0.75 & 0.81 & 103 \\
         & Improbable          & 0.92 & 0.97 & 0.95 & 322 \\
         & accuracy            &      &      & 0.92 & 425 \\
         & weighted avg        & 0.92 & 0.92 & 0.92 & 425 \\ \midrule
Pr\_Po\_Im & Probable            & 0.82 & 0.56 & 0.67 & 103 \\
         & Possible            & 0.43 & 0.74 & 0.54 & 80  \\
         & Improbable          & 0.93 & 0.86 & 0.89 & 322 \\
         & accuracy            &      &      & 0.78 & 505 \\
         & weighted avg        & 0.83 & 0.78 & 0.79 & 505 \\ \midrule
Pr\_PoIm  & Probable            & 0.77 & 0.75 & 0.76 & 103 \\
         & Possible/Improbable & 0.94 & 0.94 & 0.94 & 402 \\
         & accuracy            &      &      & 0.9  & 505 \\
         & weighted avg        & 0.9  & 0.9  & 0.9  & 505 \\ \midrule
PrPo\_Im  & Probable/Possible   & 0.85 & 0.96 & 0.9  & 183 \\
         & Improbable          & 0.97 & 0.9  & 0.94 & 322 \\
         & accuracy            &      &      & 0.92 & 505 \\
         & weighted avg        & 0.93 & 0.92 & 0.92 & 505 \\ \bottomrule
\end{tabular}
    \caption{Performance metrics across the four scenarios}
    \label{tab:performance}
\end{table}

@@

\eject
\bibliography{ai-trees-references}
